\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\KCnote{\section{Numerical Formulation}\label{section:NumericalFormulation}
The method presented here builds on that reported by \citet{jackson_2015} is known as OCVFEM formulation. The method developed is applicable to $N_{p}$ fluid phases and to the general family of $P_{n+1}(DG)-P_{n}(DG)$ element pair consistent dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces. These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a continuous representation of pressure. The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (fig.\ref{fig:fem_elem})  , which are limited to yield bounded fields.

\begin{figure}[h]
\centering
\includegraphics[width=.5\textwidth]{./Pics/P1DGP2_ele.png}
\caption{Porosity $\phi$, and permeability K are associated to the elements. The velocity nodes are associated to the element corners and the mid-points of the element edges as described in fig.\ref{fig:fem_cv}; pressure nodes are associated to the corners of the elements. The three CVs fit into a $2$D element. Saturation and saturation-dependent variables are stored CV-wise.}
\label{fig:fem_elem}
\end{figure}

@@

\begin{equation}
\begin{aligned}
\sum_{\alpha=1}^{N_{p}} {\int_{\Omega_{CVi}}} \! M_{i} \, \frac{\phi(S_{\alpha i}^{n+1})-(S_{\alpha i}^{n})}{\Delta t} dv + \\
& \cap \oint_{\Gamma_{CVi}} [\theta^{n+1/2}\; n\dot\;v_{p}^{n+1}S_{p}^{n+1}\;+\;(1-)\theta^{n+1/2}\;v_{p}^{n}S_{p}^{n}] d\Gamma \;- \\
& \cap \;\int_{\Omega_{CVi}} M_{i}q_{\alpha}^{n+\theta}dV\; }=0
\end{aligned}
\label{global_mass_balance}
\end{equation}

where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, n is normal vector of the CV and $\theta$ varies smoothly between $0.5$ (corresponding to CN) and $1$ (corresponding to BE) to avoid the introduction of spurious oscillations for large grid Courant numbers. The Eq.\ref{global_mass_balance} can be expressed in amtrix form at time level $n+1$ as
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
\medskip
As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits, are those that occur under highly critical conditions. Under this assumption, viscous fingering is no exception. It is a viscous driven hydrodynamic instability that results the collapse of the uniform interface between the fluids of different viscosity. This type of instability can be found across many research areas, disciplines and scales. Starting from small scale flow instabilities in Hele-Shaw cells that can provide the basic mathematical model, to coupled chromatographic separation systems for chemical and medical applications and reaching up to large scale reservoir systems,  such as the removal of oil from reservoirs, the potential use of CO$_2$ sequestration and the re-mediation of spills, or the transport of pollutants in aquifers. The primary removal of oil from reservoirs leaves the porous reservoirs with remaining oil that can only be removed by the use of enhanced oil-recovery (EOR). This secondary and tertiary removal of oil from porous beds is required to be as efficient and economically viable as possible.

@@

\end{enumerate} 
}
}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.5\textwidth]{./Pics1/mr1_fixed/permeability.png}
\caption{2D domain that consist of five regions with 5 different absolute permeabilities as these are represented with different colors.}
\label{fig:5regions_domain}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\subfigure[MR1 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.png}
}%
\subfigure[MR10 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.png}
}\\
\subfigure[MR1 fixed mesh middle]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.png}
}%
\subfigure[MR10 fixed mesh middle]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.png}
}\\
\subfigure[MR1 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.png}
}\\
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.png}
}\\
\end{center}
\caption{Comparing MR1 and MR10 cases using fixed mesh. Simulation time step increases from top to bottom and from t=100(start) to t=3000(end).}
\label{fig:1testcase}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\subfigure[MR10 fixed mesh start]{%
\label{fig:first}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.png}
}%
\subfigure[MR10 adapt mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.png}
}\\
\subfigure[MR10 fixed mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.png}
}%
\subfigure[MR10 adapt mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.png}
}\\
\subfigure[MR10 fixed mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.png}
}%
\subfigure[MR10 adapt mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.png}
}\\ 
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.png}
}\\
\subfigure[MR10 adapt mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.png}
}\\
\end{center}
\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h). When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time. }
\label{fig:2testcase}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\subfigure[MR10 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.png}
}%
\subfigure[MR10 fixed adapt start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.png}
}\\
\subfigure[MR10 fixed mesh t=1500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.png}
}%
\subfigure[MR10 fixed adapt t=1500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.png}
}\\
\subfigure[MR10 fixed mesh t=7500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_2000.png}
}%
\subfigure[MR10 fixed adapt t=7500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_2000.png}
}\\ 
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.png}
}\\
\subfigure[MR10 fixed adapt end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_end.png}
}\\
\end{center}
\caption{Comparing the MR=$10$, between single and double injection of fluid $1$ under the adaptive and unstructured mesh for the same time steps, t=100(a,b), t=1500(c,d), t=7500(e,f), t=10000(g,h) }
\label{fig:3testcase}
\end{figure}

@@

\begin{figure}[H]
%\begin{center}
\centering
\subfigure[MR100 fixed mesh t=500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.png}
}%
\subfigure[MR100 fixed mesh t=1500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.png}
}%
\subfigure[MR100 fixed mesh t=3000]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.png}
}\\ 
\subfigure[MR100 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.png}
}\\
%\end{center}
\caption{snapshots when the MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
\label{fig:4testcase}
\end{figure}

\begin{figure}[H]
\begin{center}
\subfigure[MR1]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR1.png}
}%
\subfigure[Recovery for MR1]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR1_1.png}
}\\
\subfigure[MR10]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR10.png}
}%
\subfigure[Recovery for MR10]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR10_10.png}
}\\
\subfigure[MR100]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR100_100_start.png}
}%
\subfigure[Recovery for MR100]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR100_100.png}
}\\ 
\end{center}
\caption{Comparison of different MR's and their recovery rates. The comparison among the MR = $1$,MR = $10$ and MR = $100$ has been done using the boundary conditions and set upt as this has already been describe in the beginning of the section \ref{section:results}. }
\label{fig:recoveryrates}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Formulation}\label{section:NumericalFormulation}
The method presented here builds on that reported by \citet{jackson_2015} is known as OCVFEM formulation. The method developed is applicable to $N_{p}$ fluid phases and to the general family of $P_{n+1}(DG)-P_{n}(DG)$ element pair consistent dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces. These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a continuous representation of pressure. The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (fig.\ref{fig:fem_elem})  , which are limited to yield bounded fields.

\begin{figure}[h] 
\centering
\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.PNG}
\caption{Porosity $\phi$, and permeability K are associated to the elements. The velocity nodes are associated to the element corners and the mid-points of the element edges as described in fig.\ref{fig:fem_cv}; pressure nodes are associated to the corners of the elements. The three CVs fit into a $2$D element. Saturation and saturation-dependent variables are stored CV-wise.}
\label{fig:fem_elem}
\end{figure}

@@

\begin{eqnarray}
 && \sum_{\alpha=1}^{N_{p}} \int\limits_{\Omega_{CVi}} \; M_{i} \, \frac{\phi\left(S_{\alpha i}^{n+1}\right)-\left(S_{\alpha i}^{n}\right)}{\Delta t} dV  + \nonumber\\
 &&  \oint_{\Gamma_{CVi}} [\theta^{n+1/2}\; n\dot\;v_{p}^{n+1}S_{p}^{n+1}\;+\;(1-)\theta^{n+1/2}\;v_{p}^{n}S_{p}^{n}] d\Gamma \;- \nonumber\\
 &&  \int_{\Omega_{CVi}} M_{i}q_{\alpha}^{n+\theta}dV\; =0
\label{global_mass_balance}
\end{eqnarray}

where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, n is normal vector of the CV and $\theta$ varies smoothly between $0.5$ (corresponding to CN) and $1$ (corresponding to BE) to avoid the introduction of spurious oscillations for large grid Courant numbers. The Eq.\ref{global_mass_balance} can be expressed in amtrix form at time level $n+1$ as

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
\medskip
As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits, are those that occur under highly critical conditions. Under this assumption, viscous fingering is no exception. It is a viscous driven hydrodynamic instability that results the collapse of the uniform interface between the fluids of different viscosity. This type of instability can be found across many research areas, disciplines and scales. Starting from small scale flow instabilities in Hele-Shaw cells that can provide the basic mathematical model, to coupled chromatographic separation systems for chemical and medical applications and reaching up to large scale reservoir systems,  such as the removal of oil from reservoirs, the potential use of CO$_2$ sequestration and the re-mediation of spills, or the transport of pollutants in aquifers. The primary removal of oil from reservoirs leaves the porous reservoirs with remaining oil that can only be removed by the use of enhanced oil-recovery (EOR). This secondary and tertiary removal of oil from porous beds is required to be as efficient and economically viable as possible.

@@

\end{enumerate} 
}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.5\textwidth]{./Pics1/mr1_fixed/permeability.png}
\caption{2D domain that consist of five regions with 5 different absolute permeabilities as these are represented with different colors.}
\label{fig:5regions_domain}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\subfigure[MR1 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.png}
}%
\subfigure[MR10 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.png}
}\\
\subfigure[MR1 fixed mesh middle]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.png}
}%
\subfigure[MR10 fixed mesh middle]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.png}
}\\
\subfigure[MR1 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.png}
}\\
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.png}
}\\
\end{center}
\caption{Comparing MR1 and MR10 cases using fixed mesh. Simulation time step increases from top to bottom and from t=100(start) to t=3000(end).}
\label{fig:1testcase}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[MR10 fixed mesh start]{%
\label{fig:first}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.png}
}%
\subfigure[MR10 adapt mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.png}
}\\
\subfigure[MR10 fixed mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.png}
}%
\subfigure[MR10 adapt mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.png}
}\\
\subfigure[MR10 fixed mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.png}
}%
\subfigure[MR10 adapt mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.png}
}\\ 
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.png}
}\\
\subfigure[MR10 adapt mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.png}
}\\
\end{center}
\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h). When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time. }
\label{fig:2testcase}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[MR10 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.png}
}%
\subfigure[MR10 fixed adapt start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.png}
}\\
\subfigure[MR10 fixed mesh t=1500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.png}
}%
\subfigure[MR10 fixed adapt t=1500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.png}
}\\
\subfigure[MR10 fixed mesh t=7500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_2000.png}
}%
\subfigure[MR10 fixed adapt t=7500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_2000.png}
}\\ 
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.png}
}\\
\subfigure[MR10 fixed adapt end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_end.png}
}\\
\end{center}
\caption{Comparing the MR=$10$, between single and double injection of fluid $1$ under the adaptive and unstructured mesh for the same time steps, t=100(a,b), t=1500(c,d), t=7500(e,f), t=10000(g,h) }
\label{fig:3testcase}
\end{figure}

@@

\begin{figure}[h]
%\begin{center}
\centering
\subfigure[MR100 fixed mesh t=500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.png}
}%
\subfigure[MR100 fixed mesh t=1500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.png}
}%
\subfigure[MR100 fixed mesh t=3000]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.png}
}\\ 
\subfigure[MR100 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.png}
}\\
%\end{center}
\caption{snapshots when the MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
\label{fig:4testcase}
\end{figure}

\begin{figure}[h] 
\begin{center}
\subfigure[MR1]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR1.png}
}%
\subfigure[Recovery for MR1]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR1_1.png}
}\\
\subfigure[MR10]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR10.png}
}%
\subfigure[Recovery for MR10]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR10_10.png}
}\\
\subfigure[MR100]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR100_100_start.png}
}%
\subfigure[Recovery for MR100]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR100_100.png}
}\\ 
\end{center}
\caption{Comparison of different MR's and their recovery rates. The comparison among the MR = $1$,MR = $10$ and MR = $100$ has been done using the boundary conditions and set upt as this has already been describe in the beginning of the section \ref{section:results}. }
\label{fig:recoveryrates}
\end{figure}
